Consistent ecosystem functional response during five years of drought and deluge in a sagebrush steppe

### 2017-07-19 manuscript/usses_water_ms.Rmd
adds discussion points

>>>>

<!---
NOTES FROM MEETING WITH PETER
1. Bet hedgers -- dominant species here deal well with low water and interannual variability; they live in dry and variable in environment, which has selected for tratis (not hitting physiological thresholds which only becom apparaent when species really go for it). Bet hedging = do the same things every year.
2. Statistical explanation -- either (1) above explains our weak and variable relationship, or we just looked at the wrong thing; lots of other things beyond VWC that are influencing ANPP.
3. Limitation -- snow, we don't know what happens. Its blowing around, who knows how big of an impact this has.
4. Show Fig 2D with real model fits and move to results figure 3.
---->
